Viscous Transport in Eroding Porous Media

### 2019-08-05 docs/transport/erosion_transport.tex
add new figs in transport paper

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to six porosities.}
\end{figure}

>>>>

\begin{figure}[H]
\center
\includegraphics*[width =0.45\linewidth]{./figs/20b_first_moment}
\includegraphics*[width =0.45\linewidth]{./figs/20b_second_moment}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to six porosities and the reference line of 100\% porosity.}
\end{figure}
